### 2024-02-07 README.Rmd
2.2.2

`r badge_custom(x = "arXiv", y = "abs/2106.10539", color = "yellow", url = "https://arxiv.org/abs/2106.10539")` 
`r badge_cran_release("fasano.franceschini.test", "orange")`
`r badge_devel("braunlab-nu/fasano.franceschini.test", "blue")` 
`r badge_cran_download("fasano.franceschini.test", "grand-total", "green")`
`r badge_github_actions("braunlab-nu/fasano.franceschini.test")`
<!-- badges: end -->

The `fasano.franceschini.test` package is an R implementation of the multidimensional Kolmogorov-Smirnov two-sample test as defined by Fasano and Franceschini (1987).

```
Fasano, G. & Franceschini, A. (1987). A multidimensional version of the
Kolmogorov-Smirnov test. Monthly Notices of the Royal Astronomical Society,
225:155-170. doi: 10.1093/mnras/225.1.155.
```

@@

You can install the released version of the `fasano.franceschini.test` package from [CRAN](https://cran.r-project.org/) with:

``` r
install.packages("fasano.franceschini.test")
```

The development version of the `fasano.franceschini.test` package can be installed from Github with:

``` r
# install.packages("devtools")
devtools::install_github("braunlab-nu/fasano.franceschini.test")
```

@@

#### Underlying distributions are the same

```{r}
library(fasano.franceschini.test)

@@

#### Underlying distributions are different

```{r}
# set seed for reproducibility
set.seed(1)

>>>>

`r badge_custom(x = "R Journal", y = "10.32614/RJ-2023-067", color = "yellow", url = "https://doi.org/10.32614/RJ-2023-067")`
`r badge_cran_release("fasano.franceschini.test", "orange")`
`r badge_devel("braunlab-nu/fasano.franceschini.test", "blue")` 
`r badge_cran_download("fasano.franceschini.test", "grand-total", "green")`
`r badge_github_actions("braunlab-nu/fasano.franceschini.test")`
<!-- badges: end -->

The `fasano.franceschini.test` package is an R implementation of the multivariate Kolmogorov-Smirnov two-sample test as defined by Fasano and Franceschini (1987).
```
Fasano, G. & Franceschini, A. (1987). A multidimensional version of the
Kolmogorov-Smirnov test. Monthly Notices of the Royal Astronomical Society,
225:155-170. doi: 10.1093/mnras/225.1.155.
```
A manuscript accompanying this package was published in The R Journal.
```
Puritz, C., Ness-Cohn, E., Braun, R. (2023). fasano.franceschini.test: An Implementation
of a Multivariate KS Test in R. The R Journal, 15(3):159-171. doi: 10.32614/RJ-2023-067.
```

@@

You can install the released version of the `fasano.franceschini.test` package from CRAN with:
``` r
install.packages("fasano.franceschini.test")
```

The development version of the `fasano.franceschini.test` package can be installed from GitHub with:
``` r
if (!require("devtools", quietly = TRUE))
    install.packages("devtools")
devtools::install_github("braunlab-nu/fasano.franceschini.test")
```

@@

#### Underlying distributions are the same
```{r}
library(fasano.franceschini.test)

@@

#### Underlying distributions are different
```{r}
# set seed for reproducibility
set.seed(1)
